---
title: "R Notebook"
output: html_notebook
---

```{r}
source("rfunctions.R")
library('knitr')
library('dplyr')
```

```{r}
# Compile simulator
run.string = paste0("gcc ppsimulator.c -lm -O2 -o ppsimulator")
system(run.string, intern = FALSE, wait = TRUE) # Compile time: a few seconds
```

# Create a single simulation {#sec-create-a-single-simulation}

-   Put the common files like input data into a `data` folder, and create separate folders for specific model definition and its corresponding results

-   The parameter should be chosen with care, otherwise the number of points would *explode*

-   Execution time is related to `U`, `W`, `H` and the `number of points`

```{r}
### parameters

# seed for Random Number Generator
SeedNum = 1 

# basic simulation parameters:
dim = 2
U = 33000
T = 6  #simulating six years
dT = 1
w = 500
H = 1

# initial input points
initial = "2015_restaurant.csv"
#initial = "xinSeed1"


# model name for saving model output
model_name = "test1"
```

```{r}
# run simulation
setwd(model_name)
run.string = paste0("../ppsimulator"," -p ../processes.txt"," -m model.txt",
                    " -i ../data/",initial," -o out_seed",toString(SeedNum),
                    " -oute 0", " -osep out_points_seed",toString(SeedNum),
                    " -U ",toString(U), " -w ",toString(w), " -H ",toString(H),
                    " -T ",toString(T)," -dT ",toString(dT),
                    " -r ",toString(SeedNum))
system(run.string, intern = FALSE, wait = TRUE)
```

```{r}
### 4) Calculate and save all second spatial moments (correlation functions)
setwd(dataDirectory)
snapshotsN <- T/dT + 2 #including the initial point at t=0, and a final point
for(i in 2:(snapshotsN-1)){  #i=1 is the initial conditions, and i=last is the same as i=last-1
  if(i<10){
    filename=paste0(nameOutPoints,"00000",i)
  } else {
    filename=paste0(nameOutPoints,"0000",i)
  }
  table=read.table(filename)
  y.coord1=get.coords.one.species.singletime(table,sp=1)
  y.coord2=get.coords.one.species.singletime(table,sp=2)
  
  dist= spx(y.coord1,y.coord1,U=U,grid.resolution=grid.resolution)[,1][2:(U/2/grid.resolution+1)];
  g11 = spx(y.coord1,y.coord1,U=U,grid.resolution=grid.resolution)[,2][2:(U/2/grid.resolution+1)];
  g12 = spx(y.coord1,y.coord2,U=U,grid.resolution=grid.resolution)[,2][2:(U/2/grid.resolution+1)];
  g22 = spx(y.coord2,y.coord2,U=U,grid.resolution=grid.resolution)[,2][2:(U/2/grid.resolution+1)];
  #g21= spx(y.coord2,y.coord1,U=U,grid.resolution=grid.resolution)[,2][2:(U/2/grid.resolution+1)];
  
  res=cbind(dist,g11,g12,g22);
  obj <- data.frame(res)
  save(obj, file = paste0(nameAllCumulants,"snapshot",toString(i),".RData"))
}
```

## Visualize results

```{r}
# Density of points
n=read.table(paste0(model_name,"/out_seed",toString(SeedNum),".counts"), header=T)
plot.species.density(n,U=U,dim=dim)
```

```{r}
# Snapshot of dynamics
snapshot=5
filename=paste0(model_name,"/out_points_seed",toString(SeedNum),"00000",snapshot)
table=read.table(filename)
coord=cbind(table$V2,table$V3)
species=table$V1
plot.points(coord,species, spch=c(1),scol=c("red","blue"),scex=c(1.5,1.5),xlab="x",ylab="y",U=U)

```

```{r}
#======== Cumulants
#Load two-point spatial moments
filename=paste0(dataDirectory, nameAllCumulants,"snapshot",snapshot,".RData")
load(filename)
x <- obj$dist
k11 <- obj$g11 #correlation function
#Load density
n=read.table(paste0(dataDirectory, nameOutDensities,".counts"),header=T)
q <- vector(length = 2)
for(sp in 1:2) {
  q[sp] <- n[,3+sp][snapshot]/U/U
}
#cumulant
c11 <- k11-q[1]*q[1]
ylim=c(-0.15,0.15)
plot(x,c11,type="l",ylim=ylim,xlim=c(0,U/2),col="red",lwd=2,ylab="g11(x)")
```
